\cursedforest\ - A Random Forest Implementation for ``Big'' and ``Wide'' Data \\ Supplementary Information

### 2017-02-09 doc/publications/plos16/plos16.tex
Reword and explain new genes

To test whether the associated features have biological meaning, we investigate whether the known BMD genes investigated
by Duncan {\it et al.}~\cite{Duncan.2011} are enriched amongst the highly ranked genes. We therefore label all variants
that fall within 100 kb of these 32 BMD genes and observe that they are ranked significantly higher than other locations
in the genome (Mann-Whitney U, $p=1.3\times10^{-07}$), supporting our hypothesis that biologically relevant features are
contributing more information to our classification model.

>>>>

To test whether the associated features have biological meaning, we investigate whether variants in or near
BMD-associated genes are enriched are enriched toward the top of our list of our ranked variant list. To begin with,
we start with 26 known BMD genes~\cite{Duncan.2011}. We also include the 6 genes that Duncan {\it et al.} find with
a new BMD association. We then add to this list the genes that Estrada {\it et al.} found with a new BMD association.
In total, this gives us a list of 100 genes.

We label our contributing variants that fall within 100 kb of these 100 genes and observe that they are ranked
significantly higher than variants from other locations in the genome (Mann-Whitney U, $p=1.3\times10^{-07}$),
supporting our hypothesis that biologically relevant features are contributing more information to our classification model.
